\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-04-09 doc/USER_MANUAL/01_introduction.tex
added paragraph from Surendra Nadh Somala to the users manual

\red{OTHER ANNOUNCEMENT: SPECFEM3D can now perform gravity field calculations in addition (or instead of) seismic wave propagation only.
See flag \texttt{GRAVITY\_INTEGRALS} in file \texttt{setup/constants.h.in}. Please also refer to \url{http://komatitsch.free.fr/preprints/GJI_Martin_gravimetry_2017.pdf}.
And yes, that is the reason why I added a falling apple on the cover of the manual :-)}\\

>>>>

\red{OTHER ANNOUNCEMENT: SPECFEM3D can now perform gravity field calculations in addition (or instead of) seismic wave propagation only.
See flag \texttt{GRAVITY\_INTEGRALS} in file \texttt{setup/constants.h.in}. Please also refer to \url{http://komatitsch.free.fr/preprints/GJI_Martin_gravimetry_2017.pdf}.
And yes, that is the reason why I added a falling apple on the cover of the manual :-).
Note that SPECFEM3D can also model transient gravity perturbations induced by earthquake rupture, as developed and explained in \cite{HaAmBaChMoSoWh2015}.
These are two different things, and both are implemented and avaible in SPECFEM3D.
To use the second feature, please refer to doc/how\_to/README\_gravity\_perturbation.txt.}\\
